 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - Cover Letter Template
% LaTeX Template
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{David}{Romeo}{ \href{mailto:Kilij65@hotmail.com}{Kilij65@hotmail.com} | \urlstyle{same}\href{https://www.linkedin.com/in/david-romeo/}{Linkedin}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     MAIN COVER LETTER CONTENT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hfill

\begin{minipage}[t]{0.5\textwidth} 
\companyname{Apple Inc}
\companyaddress{
 \\
 \\

}

\end{minipage}
\begin{minipage}[t]{0.49\textwidth} 
\currentdate{\today}
\end{minipage}

\lettercontent{Dear Recruiter,}

% The first paragraph of your job application letter should include information on why you are writing. Mention the job you are applying for and where you found the position. If you have a contact at the company, mention the person's name and your connection here.

\lettercontent{I'm thrilled about the opportunity to apply for the Technical Support position at Apple Inc. I have always had natural problem-solving skills, and working in tech support is the perfect job for my skill set. Helping clients solve technical issues and knowing that I've had a positive impact on someone each day is highly rewarding and motivating to me.} 

\lettercontent{During my previous employment at Office Superstore, I specialized in helping customers resolve a wide variety of technical issues. Over the course of my eight years of employment, I received high ratings from clients, and I helped increase customer satisfaction from 82\% to 96\%. I was praised for being highly versatile, and I was one of a select group of techs who were available to assist customers in online chats, in person and over the telephone.}

\lettercontent{I enjoy building a relationship with each client and ensuring that they receive the ultimate customer support. I'm current working towards a Computer Science degree at a local community college. I am also CompTIA A+ certified and undergo additional training twice a year to ensure that I remain up to date with the latest technical services.}

\lettercontent{Thank you for taking the time to consider my resume and cover letter. I'm looking forward to finding out more about the Technical Support position at Apple Inc. Customer service is always my top priority, and it is my goal to provide the best customer support available for each client while becoming a valuable asset at Apple Inc. If you wish to learn more about my experience and skill set, please contact me at any time.
}


   
% The next section of your cover letter should describe what you have to offer the company. Make strong connections between your abilities and the requirements listed in the job posting. Mention specifically how your skills and experience match the job. Expand on the information in your resume.
% Try to support each statement you make with a piece of evidence. Use several shorter paragraphs or bullets rather than one large block of text, which can be difficult to read and absorb quickly.
%For example 

% Using the knowledge and skills I have acquired in my <DEGREE PROGRAM> combined with my technical abilities I believe I can provide significant value to <COMPANY> while providing me invaluable experience to <PREPARE FOR OR FURTHER CAREER>.
% <RELEVANT LIFE STORY/ WORK/ PROJECT >
% In own projects, my coursework, work as a <PREVIOUS JOB TITLE> I have applied knowledge of <SUBJECT MATTER>.
% <LIST OF SMART SOUNDING SKILLS AND TOOLS>.
% Combining these tools with my interests in <FIELD> issues, I hope to help the <DEPARTMENT> answer questions about the <SUBJECT> behind <FIELD> projects.


% Conclude your application letter by thanking the employer for considering you for the position. 


\closing{Sincerely,\\  \vspace{-1cm} }

\signature{David Romeo}

\end{document}  
\documentclass[]{article}